%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Education}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {BSc Computer Science, First Class (Expected)} % Degree
    {University of Bristol} % Institution
    {Bristol, UK} % Location
    {Sep. 2019 - Jul. 2022} % Date(s)
    {
      \begin{cvitems} % Description(s) bullet points
      \item {\textbf{Dissertation: \textit{Resource Management with Reinforcement Learning}}: Implemented an OpenAI Gym environment simulating a multi-resources cluster job scheduling problem. The RL agent trained on this environment outperformed other scheduling heuristics including shortest-job-first, packer, and Tetris.}
        \item {\textbf{Relevant Courses}: High Performance Computing, Software Engineering, Computer System, Computer Architecture, Computer Graphics, Machine Learning, Computer Vision, Data-Driven Computer Science, Database and Cloud, Security, Algorithms and Data Structure.}
        \item {\textbf{Technical Skills}: Python***, C/C++***, Golang***, Java***, OpenMP**, MPI**, OpenCL*, CUDA*, NumPy**, Pandas**, SQL*, Docker*, Unity*}
        \item {\textbf{Teaching Assistant}: Year 1 Programme Seminar, Computer Systems B, Mathematics for Computer Science B, Algorithms I, Computer Architecture, Functional Programming.}
      \end{cvitems}
    }
    
  \cventry
    {Reinforcement Learning - From Theory to Practice Summer School} % Degree
    {The Alan Turing Institute} % Institution
    {London (Remote), UK} % Location
    {Jun. 2021 - Jun. 2021} % Date(s)
    {
      \begin{cvitems} % Description(s) bullet points
        \item {Learnt Upper Confidence Bound, Markov Decision Process, Q-Learning, Monte Carlo Tree Search, Deep Q-Network, Policy Gradient, etc.}
        \item {Implemented Reinforcement Learning algorithms in Python with OpenAI Gym.}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
