%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Incoming Site Reliability Engineer Intern} % Job title
    {Google} % Organization
    {London (Remote), UK} % Location
    {Jun. 2021 - Sep. 2021} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Full Stack Intern} % Job title
    {Inductosense Ltd.} % Organization
    {Bristol, UK} % Location
    {Jun. 2020 - Sep. 2020} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Constructed pages and components to detect devices and edit schedule configuration for the Electron app with React and TypeScript.}
        \item {Implemented device and schedule-related API endpoints and relevant tests used by the Electron app with C\# and .NET.}
        \item {Developed data-format transform utility to solve the issue with incompatible frontend and backend design.}
        \item {Communicated constantly with colleagues to improve the outcome of my work, e.g. product team for their expectation of the app, and peer developers to seek and provide help.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Engineering Intern} % Job title
    {Goldman Sachs} % Organization
    {London (Remote), UK} % Location
    {May. 2020 - May. 2020} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Researched into Cloud Computing and how Goldman Sachs utilises AWS to improve and expand its business with digital platforms, e.g. Marcus, Marquee, ClearFactr, etc.}
        \item {Mocked technical interview with Java and Python.}
      \end{cvitems}
    }


%---------------------------------------------------------
\end{cventries}
